\section{Scope and Positioning}
\label{sec:scope}

\sectionpurpose{This section defines the paper boundary so claims remain aligned with what is actually modeled and audited. It also states what PRISM is not.}

\sectionlearn{
\item The canonical problem solved by PRISM.
\item Explicit exclusions that prevent over-interpretation.
\item How main-paper claims are separated from supplement-level evidence.
}

PRISM is a Bayesian workflow for posterior inference on a binary event of interest. It consumes granular order-flow evidence and a calibrated machine-learning signal, then returns posterior summaries such as mean, credible intervals, and calibration diagnostics.

PRISM is not a derivative-pricing engine, not a risk-neutral valuation model, and not a claim of trading-profit superiority. Downstream decision modules may consume the posterior, but those modules are outside this paper's canonical scope.

Claims in the main paper are limited to:
\begin{itemize}[leftmargin=*]
\item workflow definition,
\item internal mathematical consistency,
\item conservative theoretical properties under explicit assumptions,
\item high-level synthetic validation summary.
\end{itemize}

Detailed stress-study outputs, finite-sample diagnostics, and scenario tables are placed in the supplement.

\sectionestablished{
\item PRISM is positioned as posterior inference workflow, not pricing model.
\item The manuscript scope is explicitly bounded.
\item Main and supplement responsibilities are separated.
}
