\section{Validation Summary}
\label{sec:validation-summary}

\sectionpurpose{This section summarizes synthetic validation outcomes at a high level and points to the supplement for full diagnostics. The summary intentionally follows audit boundaries and does not convert indeterminate scenarios into broad claims.}

\sectionlearn{
\item Which experiment families were executed.
\item Where validation is determinate versus indeterminate under current audit gates.
\item Why current evidence supports a constrained interpretation.
}

Synthetic experiments cover:
\begin{itemize}[leftmargin=*]
\item information-efficiency curves (A1),
\item convergence timing (A2),
\item strategic-timing attacks (A3),
\item correction no-regret checks (B1),
\item asymptotic-rate checks (B2),
\item misspecification-regret grids (B3),
\item regime concentration tests (B4),
\item projection impact tests (B5).
\end{itemize}

Scenario-level status in `results/**/audit.json` is mostly indeterminate for families A1, A3, B1, B2, B3, and B4 under current criteria evaluation and coverage gating. Determinate outcomes are concentrated in B5, with partial determinate support in A2.

At a high level:
\begin{itemize}[leftmargin=*]
\item A2 currently has 2 determinate passes and 8 indeterminate scenarios.
\item B5 currently has 6 determinate passes (with 3 marked paper-ready).
\item A1, A3, B1, B2, B3, and B4 are currently indeterminate at scenario level.
\item Paper-ready flags and determinacy do not coincide uniformly; both must be checked before any empirical claim.
\end{itemize}

These outcomes justify a cautious conclusion: the workflow is implementable and auditable, but broad empirical validation claims remain unsupported at family level under current determinacy patterns.

\begin{table}[t]
\centering
\begin{tabular}{lcc}
\toprule
Family & Scenario Status Pattern & Main-Paper Interpretation \\
\midrule
A1 & 9 indeterminate / 9 total & exploratory only \\
A2 & 2 pass, 8 indeterminate / 10 total & supportive but limited \\
A3 & 8 indeterminate / 8 total & stress-sensitive and unresolved \\
B1 & 20 indeterminate / 20 total & correction robustness unresolved \\
B2 & 2 indeterminate / 2 total & asymptotic rate unresolved empirically \\
B3 & 8 indeterminate / 8 total & misspecification robustness unresolved \\
B4 & 4 indeterminate / 4 total & concentration claim unresolved \\
B5 & 6 pass / 6 total (3 paper-ready) & projection behavior conditionally supported \\
\bottomrule
\end{tabular}
\caption{High-level summary computed from scenario-level `audit.json` fields (`criteria\_evaluation.overall\_pass`, `seed\_grid\_coverage.paper\_ready`).}
\label{tab:validation-summary}
\end{table}

\sectionestablished{
\item Validation evidence is mixed and must be interpreted conservatively.
\item Main text reports high-level status only; detailed diagnostics are deferred to supplement.
\item Current empirical evidence supports workflow viability, not universal claim validation.
}
